Binary companions of red giant stars in \apogee\ \DR

### 2018-02-26 paper/1-catalog/twoface-catalog.tex
More words in 3.2

If more than one posterior sample is returned after exhausting the full library
of prior samples, and the samples lie in multiple modes of the posterior pdf,
the only way to proceed is to generate more prior samples and continue running
\thejoker: these stars are flagged ``needs more prior samples.''
In this case, we generate another equal-sized library of prior samples (a total
of $2\times\nprior$ samples) and continue rejection sampling.
\todo{We note that because ... rejection sampling procedure, have to re-do
the rejection step after computing with full library of samples...}

@@

>>>>

If more than one posterior sample is returned after exhausting the full library
of prior samples, and the samples lie in multiple modes of the posterior pdf,
the only way to proceed is to generate more prior samples and continue running
\thejoker: these stars are flagged ``needs more prior samples.''
In this case, we generate another equal-sized library of prior samples (a total
of $2\times\nprior$ samples) and re-do the rejection sampling.
We note that because of the way the rejection sampling step is done, this is not
equivalent to concatenating the results from a second, independent run of
\thejoker: the log-likelihood values for all of the prior samples must be used.
If at the end of this second run the target still has fewer than \nposterior\
samples, the sampling is flagged as ``incomplete.''

@@

\todo{Fix this bit from copy-pasting}
